---
title: "Fundamentals of Computing and Data Display - Term Paper"
author: "Xuefei Li & Tianheao Wang"
date: "`r Sys.Date()`"
output:
  pdf_document:
    df_print: kable
    toc: yes
  html_document:
    df_print: paged
    toc: yes
subtitle: Understanding the "Depression" world on Twitter:an exploratory study 
references:
- author:
  - family: Wickham
    given: Hadley
  container-title: Journal of Statistical Software
  id: Wickham2014
  issue: 10
  issued:
    year: 2014
  page: 1-23
  title: Tidy Data
  type: article-journal
  volume: 59
- author:
  - family: Baumer
    given: Benjamin S.
  - family: Kaplan
    given: Daniel T.
  - family: Horton
    given: Nicholas J.
  id: Baumer2017
  issued:
    year: 2017
  publisher: Chapman \& Hall/CRC Press.
  title: Modern Data Science with R
  type: book
---

```{r, include = FALSE}
library(knitr)
library(tidyverse)
```
## Abstract

xxx

## Introduction

This section outlines the research idea. We can also cite related work here [@Wickham2014; @Baumer2017].

Note that compiled term paper (the PDF) is supposed to be more text-centered than the RMarkdown documents we used in class, i.e. the text sections are more detailed and big or redundant code chunks can be hidden.

### Research background

xxx

### Literature review

xxx

## Method

xxx

### Data sources

xxx

### Data collection

This section describes the data sources and the data gathering process.

```{r}
# A code chunk that exemplifies the data gathering process
```

```{r, include = FALSE}
# Additional code chunks that repeat tasks or do basic things can be hidden
```

## Results

This section presents the main results.

### Data exploration

The results section may have a data exploration part, but in general the structure here depends on the specific project.

```{r}
# What happens here depends on the specific project
```

```{r}
# What happens here depends on the specific project
```

### Analysis

This section presents the main results, such as (for example) stats and graphs that show relationships, model results and/or clustering, PCA, etc.

```{r}
# What happens here depends on the specific project
```

```{r}
# What happens here depends on the specific project
```

```{r}
# What happens here depends on the specific project

```

## Discussion

This section summarizes the results and may briefly outline advantages and limitations of the work presented.

### Conclusions and implications

xxx

### Limitations

xxx

## References
